---
title: "Tytuł"
author: "Michał Bojanowski"
date: "2016-03-22"
output: 
  html_document:
    toc: yes
    number_sections: yes
  word_document:
    toc: yes
    keep_md: yes
  pdf_document:
    toc: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache=FALSE
  )

set.seed(123)
```

# First section

Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. 

Now a list:

- item 1
- item 2
    + subitem
    + subitem
    + subitem
- item 3

Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. 

1. Item 1
2. Item 1
    - item 2
        + subitem
3. Item 1


```{r r_code}
x <- rnorm(100)
x
```

## Subsection with a quote

> This is a quote.


### Subsubsection

Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. 

## Subsection with figure

```{r r_figure}
hist(x)
```
